HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-25 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Tutorial of the month 2.

>>>>

In the context of web-based training, if the HSF helps to constitute a living
collection of online tutorials, we could organize regular events such as
a ``Tutorial of the month'', or some sort of ``like'' system for the students
to support their favorite tutorials. The best authors must be recognized, so
that they can showcase their most popular online tutorials, just the same as
their research publications.
